Investigation of scarid data

### 2019-06-05 r/5.8.19.Rmd

```{r, echo=F, message=F, warning=F}
library(here)
library(tidyverse)
library(mgcv)
library(MuMIn)

@@

Assemble PC1 and PC2 variables
```{r, echo=F, message=F, warning=F}
pca_pred <- prcomp(na.omit(sum_site %>% 
              select(rugosity, ma_cover, ma_canopy, ta_cover, ta_canopy, lc_cover, scar_den, scar_bm, carn30_bm)),
  center = T, scale = T)
pca_bent <- prcomp(na.omit(sum_site %>% 
              select(rugosity, ma_cover, ma_canopy, ta_cover, ta_canopy)),
  center = T, scale = T)
pca_fish <- prcomp(na.omit(sum_site %>% 
              select(scar_bm, carn30_bm)),
  center = T, scale = T)

autoplot(pca_pred, data = sum_site, shape = 'island', colour = 'island',
         loadings = T, loadings.colour = 'gray',
         loadings.label = T, loadings.label.size = 3, loadings.label.colour = 'black',
            loadings.label.repel = T) +
    scale_color_manual(values = c("cadetblue3","cadetblue3","cadetblue3")) +
    theme_bw() +
    theme(legend.title = element_blank())
ggsave(here("figs/pca_pred.png"), width = 8, height = 5)

>>>>

```{r, echo=F, message=F, warning=F}
library(here)
library(tidyverse)
library(factoextra)
library(corrplot)
library(mgcv)
library(MuMIn)

@@

Assemble PC1 and PC2 variables
```{r, echo=F, message=F, warning=F}
pca_data <- na.omit(sum_site %>%
  select(rugosity, ma_cover, ma_canopy, ta_cover, ta_canopy, lc_cover, scar_bm, scar_den, carn30_bm))
names(pca_data)[1:9] =
  c("rugosity", "macroalgal cover", "macroalgal canopy", "turf cover", "turf canopy", "coral cover", "scarid biomass", "scarid density", "predator biomass")

pca_pred <- prcomp(pca_data, center = T, scale = T)

# pca_bent <- prcomp(na.omit(sum_site %>% 
#               select(rugosity, ma_cover, ma_canopy, ta_cover, ta_canopy)), center = T, scale = T)
# pca_fish <- prcomp(na.omit(sum_site %>% 
#               select(scar_bm, carn30_bm)), center = T, scale = T)

fviz_pca_biplot(pca_pred,
                col.ind = sum_site$island,
                mean.point = F,
                label = "var",
                repel = T
                ) +
  scale_shape_manual(values=c(15,16,17)) +
  scale_color_manual(values = c("black","black","black")) +
  labs(x = "PC1 (55.6%)", y = "PC2 (24.5%)", title = "") +
  theme_bw() +
  theme(legend.title = element_blank())

ggsave(here("figs/pca_pred.png"), width = 7, height = 5)

-var <- get_pca_var(pca_pred)
corrplot(var$contrib, is.corr=FALSE)

### 2019-06-05 r/Ch2 outline_V3.Rmd

sum_site <- read.csv(here("data","sum_site.csv"), stringsAsFactors=F) %>%
  select(-X) %>% 
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island)
sum_id <- read.csv(here("data","sum_id.csv"), stringsAsFactors=F) %>%
  select(-X) %>% 
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island) %>%
  filter(fr <= 3000)
sum_ssp <- read.csv(here("data","sum_site_sp_ph.csv"), stringsAsFactors=F) %>%
  select(-X) %>% 
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island)
```

@@

```{r, eval = F, echo=F, message=F, warning=F}
ggplot(filter(sum_ssp, species_code != "rbp" & phase == "i"), aes(x=factor(site, levels = sum_site$site), y=fr_mean)) +
    geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
    geom_errorbar(aes(ymin=fr_mean-fr_se, ymax=fr_mean+fr_se), width=.2,
                 position=position_dodge(.9)) +
    facet_grid(~species) +
    scale_fill_brewer(palette = "Blues") +
    labs(title="Mean feeding rates of individuals (initial phase)", 
         y="Feeding rate (bites/hr)", 
         x="Site") +
    theme_bw() +
    theme(strip.text = element_text(face = "italic"), 
          axis.text.x = element_text(angle = 90, hjust = 1), 
          plot.title = element_text(hjust = 0.5))
```

@@

## PCA
```{r, echo=F, message=F, warning=F}
pca_pred <- prcomp(na.omit(sum_site %>% 
              select(rugosity, ma_cover, ma_canopy, ta_cover, ta_canopy, scar_den, 
                     scar_bm, carn30_bm)),
  center = T, scale = T)

@@

## GAMM results

### Predicting feeding rate:

```{r, echo=F, message=F, warning=F}
m_data <- sum_ssp_pca %>% filter(species_code!="rbp")

gamm1 <- gamm(fr_mean ~ species_code + phase + s(length_m, k=4) + s(pc1_all, k=4) + s(pc2_all, k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g1 <- c("g1", "Species + Phase + Size + PC1 + PC2", AICc(gamm1$lme), summary(gamm1$gam)$r.sq)

gamm2 <- gamm(fr_mean ~ species_code + phase + s(length_m, k=4) + s(pc1_all, k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g2 <- c("g2", "Species + Phase + Size + PC1", AICc(gamm2$lme), summary(gamm2$gam)$r.sq)

gamm3 <- gamm(fr_mean ~ species_code + phase + s(length_m, by = factor(species_code), k=4) + s(pc1_all, by = factor(species_code), k=4) + s(pc2_all, by = factor(species_code), k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g3 <- c("g3", "Species + Phase + Size~Species + PC1~Species + PC2~Species", AICc(gamm3$lme), summary(gamm3$gam)$r.sq)

gamm4 <- gamm(fr_mean ~ species_code + phase + s(length_m, by = factor(species_code), k=4) + s(pc1_all, by = factor(species_code), k=4) + s(pc2_all, k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g4 <- c("g4", "Species + Phase + Size~Species + PC1~Species + PC2", AICc(gamm4$lme), summary(gamm4$gam)$r.sq)

gamm5 <- gamm(fr_mean ~ species + phase + s(length_m, by = factor(species_code), k=4) + s(pc1_all, by = factor(species_code), k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g5 <- c("g5", "Species + Phase + Size~Species + PC1~Species", AICc(gamm5$lme), summary(gamm5$gam)$r.sq)

gamm6 <- gamm(fr_mean ~ phase + s(length_m, k=4) + s(pc1_all, by = factor(species_code), k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g6 <- c("g6", "Phase + Size + PC1~Species", AICc(gamm6$lme), summary(gamm6$gam)$r.sq)

gamm7 <- gamm(fr_mean ~ phase + s(length_m, by = factor(species_code), k=4) + s(pc1_all, k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g7 <- c("g7", "Phase + Size~Species + PC1", AICc(gamm7$lme), summary(gamm7$gam)$r.sq)

gamm8 <- gamm(fr_mean ~ species + phase + s(length_m, by = factor(species_code), k=4) + s(pc1_all, k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g8 <- c("g8", "Species + Phase + Size~Species + PC1", AICc(gamm8$lme), summary(gamm8$gam)$r.sq)

gamm9 <- gamm(fr_mean ~ species + phase + s(length_m, k=4) + s(pc1_all, by = factor(species_code), k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g9 <- c("g9", "Species + Phase + Size + PC1~Species", AICc(gamm9$lme), summary(gamm9$gam)$r.sq)

gamm10 <- gamm(fr_mean ~ species + phase + s(pc1_all, by = factor(species_code), k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g10 <- c("g10", "Species + Phase + PC1~Species", AICc(gamm10$lme), summary(gamm10$gam)$r.sq)

gamm11 <- gamm(fr_mean ~ phase + s(length_m, by = factor(species_code), k=4) + s(pc1_all, by = factor(species_code), k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g11 <- c("g11", "Phase + Size~Species + PC1~Species", AICc(gamm11$lme), summary(gamm11$gam)$r.sq)

gtab_fr <- as.data.frame(rbind(g1,g2,g3,g4,g5,g6,g7,g8,g9,g10,g11)) %>% setNames(c("g","Model", "AICc", "Adj. R2")) %>% arrange(AICc)
```

```{r, echo=F, message=F}
kable(gtab_fr[1:4, ])
plot(gamm10$gam,pages=1)
```

### Predicting feeding intensity:

```{r, echo=F, message=F, warning=F}
m_data <- sum_ssp_pca %>% filter(species_code!="rbp")

fi_gamm1 <- gamm(for_bites_mean ~ species_code + phase + s(length_m, k=4) + s(pc1_all, k=4) + s(pc2_all, k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
# summary(fi_gamm1$gam)
# plot(fi_gamm1$gam,pages=1)
g1 <- c("g1", "Species + Phase + Size + PC1 + PC2", AICc(fi_gamm1$lme), summary(fi_gamm1$gam)$r.sq)

fi_gamm2 <- gamm(for_bites_mean ~ species_code + phase + s(length_m, k=4) + s(pc1_all, k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g2 <- c("g2", "Species + Phase + Size + PC1", AICc(fi_gamm2$lme), summary(fi_gamm2$gam)$r.sq)

fi_gamm3 <- gamm(for_bites_mean ~ species_code + phase + s(length_m, by = factor(species_code), k=4) + s(pc1_all, by = factor(species_code), k=4) + s(pc2_all, by = factor(species_code), k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g3 <- c("g3", "Species + Phase + Size~Species + PC1~Species", AICc(fi_gamm3$lme), summary(fi_gamm3$gam)$r.sq)

fi_gamm4 <- gamm(for_bites_mean ~ species_code + phase + s(length_m, by = factor(species_code), k=4) + s(pc1_all, by = factor(species_code), k=4) + s(pc2_all, k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g4 <- c("g4", "Species + Phase + Size~Species + PC1~Species + PC2", AICc(fi_gamm4$lme), summary(fi_gamm4$gam)$r.sq)

fi_gamm5 <- gamm(for_bites_mean ~ phase + s(length_m, by = factor(species_code), k=4) + s(pc1_all, by = factor(species_code), k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g5 <- c("g5", "Phase + Size~Species + PC1~Species", AICc(fi_gamm5$lme), summary(fi_gamm5$gam)$r.sq)

fi_gamm6 <- gamm(for_bites_mean ~ species + phase + s(length_m, k=4) + s(pc1_all, by = factor(species_code), k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g6 <- c("g6", "Species + Phase + Size + PC1~Species", AICc(fi_gamm6$lme), summary(fi_gamm6$gam)$r.sq)

fi_gamm7 <- gamm(for_bites_mean ~ species + phase + s(length_m, by = factor(species_code), k=4) + s(pc1_all, k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g7 <- c("g7", "Species + Phase + Size~Species + PC1", AICc(fi_gamm7$lme), summary(fi_gamm7$gam)$r.sq)

fi_gamm8 <- gamm(for_bites_mean ~ phase + s(length_m, k=4) + s(pc1_all, by = factor(species_code), k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g8 <- c("g8", "Phase + Size + PC1~Species", AICc(fi_gamm8$lme), summary(fi_gamm8$gam)$r.sq)

fi_gamm9 <- gamm(for_bites_mean ~ phase + s(length_m, by = factor(species_code), k=4) + s(pc1_all, k=4), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
g9 <- c("g9", "Phase + Size~Species + PC1", AICc(fi_gamm9$lme), summary(fi_gamm9$gam)$r.sq)

gtab_fi <- as.data.frame(rbind(g1,g2,g3,g4,g5,g6,g7,g8,g9)) %>% setNames(c("g", "Model", "AICc", "Adj. R2")) %>% arrange(AICc)
```

```{r, echo=F, message=F}
kable(gtab_fi[1:3, ])
plot(gamm6$gam,pages=1)
```

>>>>

sum_site <- read.csv(here("data","sum_site.csv"), stringsAsFactors=F) %>%
  select(-X) %>% 
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island)
sum_id <- read.csv(here("data","sum_id.csv"), stringsAsFactors=F) %>%
  select(-X) %>% 
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island) %>%
  filter(fr <= 3000)
sum_ssp <- read.csv(here("data","sum_ssp.csv"), stringsAsFactors=F) %>%
  select(-X) %>% 
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island)
```

@@

```{r, eval = F, echo=F, message=F, warning=F}
ggplot(filter(sum_ssp, species_code != "rbp" & phase == "i"), aes(x=factor(site, levels = sum_site$site), y=fr_mean)) +
    geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
    geom_errorbar(aes(ymin=fr_mean-fr_se, ymax=fr_mean+fr_se), width=.2,
                 position=position_dodge(.9)) +
    facet_grid(~species) +
    scale_fill_brewer(palette = "Blues") +
    labs(title="Mean feeding rates of individuals (initial phase)", 
         y="Feeding rate (bites/min)", 
         x="Site") +
    theme_bw() +
    theme(strip.text = element_text(face = "italic"), 
          axis.text.x = element_text(angle = 90, hjust = 1), 
          plot.title = element_text(hjust = 0.5))
```

@@

## PCA
```{r, echo=F, message=F, warning=F}
pca_pred <- prcomp(na.omit(sum_site %>% 
              select(rugosity, ma_cover, ma_canopy, ta_cover, ta_canopy, scar_den, 
                     scar_bm, carn30_bm, lc_cover)),
  center = T, scale = T)

@@

## GAMM results (see 5.8.19)

### 2019-06-05 r/Follows.Rmd

# Summarizing data by site, species, and phase
Next I create a summary tables that average variables within each site/species/phase, then combines into one table
```{r,warning=FALSE, message= FALSE}
# site averages
sum_site <- sum_id %>% 
  filter(length_cm >= 15 & length_cm <= 30) %>%
  group_by(site,island) %>% 
  summarize(
    n=n(),
    g_frac_mean=mean(g_frac),
    g_frac_se=sd(g_frac)/sqrt(n),
    br_mean=mean(br,na.rm=TRUE),
    br_se=sd(br,na.rm=TRUE)/sqrt(n),
    fr_mean=mean(fr),
    fr_se=sd(fr)/sqrt(n),
    for_dur_mean=mean(for_dur,na.rm=TRUE),
    for_dur_se=sd(for_dur,na.rm=TRUE)/sqrt(n),
    for_bites_mean=mean(for_bites,na.rm=TRUE),
    for_bites_se=sd(for_bites,na.rm=TRUE)/sqrt(n),
    int_tot_mean=mean(int_tot),
    int_tot_se=sd(int_tot)/sqrt(n),
    int_scar_mean=mean(int_scar),
    int_scar_se=sd(int_scar)/sqrt(n),
    int_con_mean=mean(int_con),
    int_con_se=sd(int_con)/sqrt(n),
    int_hetscar_mean=mean(int_hetscar),
    int_hetscar_se=sd(int_hetscar)/sqrt(n),
    int_dam_mean=mean(int_dam),
    int_dam_se=sd(int_dam)/sqrt(n)
    ) %>% 
  select(-n)

# site averages by species
sum_ss <- sum_id %>% 
  filter(length_cm >= 15 & length_cm <= 30) %>%
  group_by(site, island, species, species_code) %>% 
  summarize(
    n=n(),
    g_frac_mean=mean(g_frac),
    g_frac_se=sd(g_frac)/sqrt(n),
    br_mean=mean(br,na.rm=TRUE),
    br_se=sd(br,na.rm=TRUE)/sqrt(n),
    fr_mean=mean(fr),
    fr_se=sd(fr)/sqrt(n),
    for_dur_mean=mean(for_dur,na.rm=TRUE),
    for_dur_se=sd(for_dur,na.rm=TRUE)/sqrt(n),
    for_bites_mean=mean(for_bites,na.rm=TRUE),
    for_bites_se=sd(for_bites,na.rm=TRUE)/sqrt(n), 
    int_tot_mean=mean(int_tot),
    int_tot_se=sd(int_tot)/sqrt(n), 
    int_scar_mean=mean(int_scar),
    int_scar_se=sd(int_scar)/sqrt(n), 
    int_con_mean=mean(int_con),
    int_con_se=sd(int_con)/sqrt(n), 
    int_hetscar_mean=mean(int_hetscar),
    int_hetscar_se=sd(int_hetscar)/sqrt(n), 
    int_dam_mean=mean(int_dam),
    int_dam_se=sd(int_dam)/sqrt(n)
    )

# site averages by species and phase
sum_ssp <- sum_id %>% 
  filter(length_cm >= 15 & length_cm <= 30) %>%
  group_by(site, island, species, species_code, phase) %>% 
  summarize(
    n=n(),
    g_frac_mean=mean(g_frac),
    g_frac_se=sd(g_frac)/sqrt(n),
    br_mean=mean(br,na.rm=TRUE),
    br_se=sd(br,na.rm=TRUE)/sqrt(n),
    fr_mean=mean(fr),
    fr_se=sd(fr)/sqrt(n),
    for_dur_mean=mean(for_dur,na.rm=TRUE),
    for_dur_se=sd(for_dur,na.rm=TRUE)/sqrt(n),
    for_bites_mean=mean(for_bites,na.rm=TRUE),
    for_bites_se=sd(for_bites,na.rm=TRUE)/sqrt(n), 
    int_tot_mean=mean(int_tot),
    int_tot_se=sd(int_tot)/sqrt(n),
    int_scar_mean=mean(int_scar),
    int_scar_se=sd(int_scar)/sqrt(n),
    int_con_mean=mean(int_con),
    int_con_se=sd(int_con)/sqrt(n), 
    int_hetscar_mean=mean(int_hetscar),
    int_hetscar_se=sd(int_hetscar)/sqrt(n),
    int_dam_mean=mean(int_dam),
    int_dam_se=sd(int_dam)/sqrt(n),
    length_m = mean(length_cm),
    length_se = sd(length_cm)/sqrt(n)
    )
```

>>>>

# Summarizing data by site, species, and phase
Next I create a summary tables that average variables within each site/species/phase, then combines into one table
```{r,warning=FALSE, message= FALSE}
# site averages
sum_site <- sum_id %>% 
  filter(length_cm >= 15 & length_cm <= 30) %>%
  group_by(site,island) %>% 
  summarize(
    n=n(),
    g_frac_mean=mean(g_frac),
    g_frac_median=median(g_frac),
    g_frac_se=sd(g_frac)/sqrt(n),
    br_mean=mean(br,na.rm=TRUE),
    br_median=median(br,na.rm=TRUE),
    br_se=sd(br,na.rm=TRUE)/sqrt(n),
    fr_mean=mean(fr),
    fr_median=median(fr),
    fr_se=sd(fr)/sqrt(n),
    for_dur_mean=mean(for_dur,na.rm=TRUE),
    for_dur_median=median(for_dur,na.rm=TRUE),
    for_dur_se=sd(for_dur,na.rm=TRUE)/sqrt(n),
    for_bites_mean=mean(for_bites,na.rm=TRUE),
    for_bites_median=median(for_bites,na.rm=TRUE),
    for_bites_se=sd(for_bites,na.rm=TRUE)/sqrt(n),
    int_tot_mean=mean(int_tot),
    int_tot_median=median(int_tot),
    int_tot_se=sd(int_tot)/sqrt(n),
    int_scar_mean=mean(int_scar),
    int_scar_median=median(int_scar),
    int_scar_se=sd(int_scar)/sqrt(n),
    int_con_mean=mean(int_con),
    int_con_median=median(int_con),
    int_con_se=sd(int_con)/sqrt(n),
    int_hetscar_mean=mean(int_hetscar),
    int_hetscar_median=median(int_hetscar),
    int_hetscar_se=sd(int_hetscar)/sqrt(n),
    int_dam_mean=mean(int_dam),
    int_dam_median=median(int_dam),
    int_dam_se=sd(int_dam)/sqrt(n)
    ) %>% 
  select(-n)

# site averages by species
sum_ss <- sum_id %>% 
  filter(length_cm >= 15 & length_cm <= 30) %>%
  group_by(site, island, species, species_code) %>% 
  summarize(
    n=n(),
    length_mean=mean(length_cm),
    length_se=sd(length_cm)/sqrt(n),
    g_frac_mean=mean(g_frac),
    g_frac_median=median(g_frac),
    g_frac_se=sd(g_frac)/sqrt(n),
    br_mean=mean(br,na.rm=TRUE),
    br_median=median(br,na.rm=TRUE),
    br_se=sd(br,na.rm=TRUE)/sqrt(n),
    fr_mean=mean(fr),
    fr_median=median(fr),
    fr_se=sd(fr)/sqrt(n),
    for_dur_mean=mean(for_dur,na.rm=TRUE),
    for_dur_median=median(for_dur,na.rm=TRUE),
    for_dur_se=sd(for_dur,na.rm=TRUE)/sqrt(n),
    for_bites_mean=mean(for_bites,na.rm=TRUE),
    for_bites_median=median(for_bites,na.rm=TRUE),
    for_bites_se=sd(for_bites,na.rm=TRUE)/sqrt(n),
    int_tot_mean=mean(int_tot),
    int_tot_median=median(int_tot),
    int_tot_se=sd(int_tot)/sqrt(n),
    int_scar_mean=mean(int_scar),
    int_scar_median=median(int_scar),
    int_scar_se=sd(int_scar)/sqrt(n),
    int_con_mean=mean(int_con),
    int_con_median=median(int_con),
    int_con_se=sd(int_con)/sqrt(n),
    int_hetscar_mean=mean(int_hetscar),
    int_hetscar_median=median(int_hetscar),
    int_hetscar_se=sd(int_hetscar)/sqrt(n),
    int_dam_mean=mean(int_dam),
    int_dam_median=median(int_dam),
    int_dam_se=sd(int_dam)/sqrt(n)
    )

# site averages by species and phase
sum_ssp <- sum_id %>% 
  filter(length_cm >= 15 & length_cm <= 30) %>%
  group_by(site, island, species, species_code, phase) %>% 
  summarize(
    n=n(),
    length_mean=mean(length_cm),
    length_se=sd(length_cm)/sqrt(n),
    g_frac_mean=mean(g_frac),
    g_frac_median=median(g_frac),
    g_frac_se=sd(g_frac)/sqrt(n),
    br_mean=mean(br,na.rm=TRUE),
    br_median=median(br,na.rm=TRUE),
    br_se=sd(br,na.rm=TRUE)/sqrt(n),
    fr_mean=mean(fr),
    fr_median=median(fr),
    fr_se=sd(fr)/sqrt(n),
    for_dur_mean=mean(for_dur,na.rm=TRUE),
    for_dur_median=median(for_dur,na.rm=TRUE),
    for_dur_se=sd(for_dur,na.rm=TRUE)/sqrt(n),
    for_bites_mean=mean(for_bites,na.rm=TRUE),
    for_bites_median=median(for_bites,na.rm=TRUE),
    for_bites_se=sd(for_bites,na.rm=TRUE)/sqrt(n),
    int_tot_mean=mean(int_tot),
    int_tot_median=median(int_tot),
    int_tot_se=sd(int_tot)/sqrt(n),
    int_scar_mean=mean(int_scar),
    int_scar_median=median(int_scar),
    int_scar_se=sd(int_scar)/sqrt(n),
    int_con_mean=mean(int_con),
    int_con_median=median(int_con),
    int_con_se=sd(int_con)/sqrt(n),
    int_hetscar_mean=mean(int_hetscar),
    int_hetscar_median=median(int_hetscar),
    int_hetscar_se=sd(int_hetscar)/sqrt(n),
    int_dam_mean=mean(int_dam),
    int_dam_median=median(int_dam),
    int_dam_se=sd(int_dam)/sqrt(n)
    )
```

### 2019-06-05 r/Sites.Rmd

```{r,message=F,warning=F}
# Total scarids
scar_tran <- fish %>% 
  filter(family=="Scaridae",
         biomass != 0) %>% 
  group_by(site,transect) %>% 
  summarize(
    bm_t=sum(biomass)/1.2,
    den_t=n()/1.2,
    l_t=mean(length)
    ) %>% 
  right_join(exp_tran,by=c("site","transect")) %>%
  mutate_each(funs(replace(.,is.na(.),0)), -l_t)

>>>>

```{r,message=F,warning=F}
# Total scarids
scar_tran <- fish %>% 
  filter(family=="Scaridae",
         biomass != 0,
         length > 5) %>% 
  group_by(site,transect) %>% 
  summarize(
    bm_t=sum(biomass)/1.2,
    den_t=n()/1.2,
    l_t=mean(length)
    ) %>% 
  right_join(exp_tran,by=c("site","transect")) %>%
  mutate_each(funs(replace(.,is.na(.),0)), -l_t)

### 2019-06-05 r/old drafts/Data_prodding.Rmd

```{r,echo=FALSE}
panel.cor <- function(x, y, digits=2, prefix="", cex.cor, ...)
{
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(0, 1, 0, 1))
    r <- abs(cor(x, y))
    txt <- format(c(r, 0.123456789), digits=digits)[1]
    txt <- paste(prefix, txt, sep="")
    if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
    text(0.5, 0.5, txt, cex = cex.cor * r)
}
pairs(~consp_l+scar_bm+carn30_bm+rugosity+ma_ind+ta_canopy+ta_cover, data=sum_id,
      lower.panel=panel.smooth, upper.panel=panel.cor, 
      pch=20, main="Selected Fish & Benthic Community Variables", na.action = na.omit)
```

>>>>

```{r,echo=FALSE}
panel.cor <- function(x, y, digits=2, prefix="", cex.cor, ...)
{
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(0, 1, 0, 1))
    r <- abs(cor(x, y))
    txt <- format(c(r, 0.123456789), digits=digits)[1]
    txt <- paste(prefix, txt, sep="")
    if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
    text(0.5, 0.5, txt, cex = cex.cor * r)
}
pairs(~consp_l+scar_bm+carn30_bm+carn30_den+rugosity+ma_ind+ta_canopy+ta_cover, data=sum_id,
      lower.panel=panel.smooth, upper.panel=panel.cor, 
      pch=20, main="Selected Fish & Benthic Community Variables", na.action = na.omit)
```
